---
title: "NEISS Analysis"
author: "BIFX 552 class"
date: "9/28/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readxl)

# Read in NEISS data
year <- 2016
dat <- read_excel('~/data/NEISS-data-2016-updated-APRIL2017.xlsx') %>%
       mutate(age = ifelse(age > 200, (age - 200) / 12, age), # age > 200 is coded in months since birth + 200
              male = ifelse(sex > 0, sex == 1, NA)) # 1 = Male, 2 = Female, 0 = Unknown
```

# NEISS Analysis

This is an example html file that was generated from R. This data set comes from the [Consumer Product Safety Commission](https://www.cpsc.gov/Research--Statistics), and contains data from the National Electronic Injury Surveillance System (NEISS). For more information on codes, see the [NEISS Coding Manual](https://www.cpsc.gov/s3fs-public/2017NEISSCodingManualCPSConlyNontrauma.pdf). It is important to note, for example, that a child aged nine months will have an age code of 209. You might find some of the ages suspicious if you didn't know that.

## 6-year-olds with arm injuries

# Males
```{r males, echo=FALSE}
n6yoM <- {filter(dat, age == 6 & male & 
                  body_part %in% c(33,80)) %>%
          dim()}[1] # return the number of rows

# this is another way of doing the same thing
n6yoM <- filter(dat, age == 6 & male & 
                  body_part %in% c(33,80))[[1]] %>%
         length() # return the number of rows

# yet another way of doing the same thing
n6yoM <- with(dat, age == 6 & male & 
                   body_part %in% c(33,80)) %>%
         sum() # return the number of rows

```

There were `r n6yoM` 6-year-old males who were captured in the NEISS dataset in `r year`.


# Females

# Discussion
